---
output:
  word_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---

```{r include = FALSE}
library(tidyverse)
library(tidymodels)
library(mice)
library(VIM)
library(ranger)
library(randomForest)
library(caret)
library(gridExtra)
library(vip)
library(skimr)
```

```{r }
drug <- read_csv("drug_data-1.csv")
```


```{r }
names(drug) =c("ID", "Age", "Gender", "Education", "Country", "Ethnicity","Nscore", "Escore", "Oscore", "Ascore", "Cscore", "Impulsive","SS", "Alcohol", "Amphet", "Amyl", "Benzos", "Caff", "Cannabis","Choc", "Coke", "Crack", "Ecstasy", "Heroin", "Ketamine", "Legalh","LSD", "Meth", "Mushrooms", "Nicotine", "Semer", "VSA")
#str(drug)

drug[drug=="CL0"] = "No"
drug[drug=="CL1"] = "No"
drug[drug=="CL2"] = "Yes"
drug[drug=="CL3"] = "Yes"
drug[drug=="CL4"] = "Yes"
drug[drug=="CL5"] = "Yes"
drug[drug=="CL6"] = "Yes"

```

```{r}
drug_clean = drug%>% mutate_at(vars(Age:Ethnicity),funs(as_factor))%>%mutate(Age =factor(Age, labels =c("18_24", "25_34", "35_44","45_54", "55_64", "65_")))%>%mutate(Gender =factor(Gender, labels =c("Male", "Female")))%>%mutate(Education =factor(Education, labels =c("Under16", "At16", "At17", "At18", "SomeCollege","ProfessionalCert", "Bachelors", "Masters", "Doctorate")))%>%mutate(Country =factor(Country,labels =c("USA", "NewZealand", "Other", "Australia","Ireland","Canada","UK")))%>%mutate(Ethnicity =factor(Ethnicity,labels =c("Black", "Asian", "White", "White/Black", "Other","White/Asian", "Black/Asian")))%>%
mutate_at(vars(Alcohol:VSA),funs(as_factor))%>%select(-ID)

```

```{r}
#str(drug_clean)
```

```{r}
drug_clean= drug_clean%>% select(!(Alcohol:Mushrooms))%>%
  select(!(Semer:VSA))
names(drug_clean)
```

```{r Task 1}

skim(drug_clean)

```

Checking the data, there is no missingness within the set.

```{r Task 2}
set.seed(1234)
nicotine_split = initial_split(drug_clean, prob = 0.70, strata = Nicotine)
train = training(nicotine_split)
test = testing(nicotine_split)

```


```{r Task 3}

p1 = ggplot(train, aes(x = Age, fill = Nicotine)) + geom_bar(position = "fill")
p2 = ggplot(train, aes(x = Gender, fill = Nicotine)) + geom_bar(position = "fill")
p3 = ggplot(train, aes(x = Education, fill = Nicotine)) + geom_bar(position = "fill")
p4 = ggplot(train, aes(x = Country, fill = Nicotine)) + geom_bar(position = "fill")

grid.arrange(p1,p2,p3,p4)
```


```{r Task 3v2}
p5 = ggplot(train, aes(x = Ethnicity, fill = Nicotine)) + geom_bar(position = "fill")
p6 = ggplot(train, aes(x = Nicotine, y = Nscore)) + geom_boxplot()
p7 = ggplot(train, aes(x = Nicotine, y = Escore)) + geom_boxplot()
p8 = ggplot(train, aes(x = Nicotine, y = Oscore)) + geom_boxplot()

grid.arrange(p5,p6,p7,p8)
```

```{r}
p9 = ggplot(train, aes(x = Nicotine, y = Ascore)) + geom_boxplot()
p10 = ggplot(train, aes(x = Nicotine, y = Cscore)) + geom_boxplot()
p11 = ggplot(train, aes(x = Nicotine, y = Impulsive)) + geom_boxplot()
p12 = ggplot(train, aes(x = Nicotine, y = SS)) + geom_boxplot()

grid.arrange(p9,p10,p11,p12)
```

Looking at the 12 variables and their relation to nicotine, some correspond with consumption more than others. Age does play a role in consumption. We can see that the younger age ranges, like 18 to 24, consume more nicotine than someone in the age range 65 or older. With gender, men are only slightly more likely than females to consume nicotine and the higher level of education you receive the less you consume. Country does appear significant, but only when it comes to the UK and that someone is less likely to consume nicotine if they are from there. Someone that is white/Asian or white/black are significantly more likely than someone who is black or Asian to consume nicotine. But only slightly more likely than someone white, black/Asian or classified as other. Escore will not have any role in predicting nicotine consumption. Nscore, Oscore, Ascore, and Cscore all have about the same relation to nicotine, don't give us too much insight. Impulsively only slightly nods towards nicotine usage, while sensation seeking will significantly cause someone to use nicotine.


```{r Task 4v1}

set.seed(123)
rf_folds = vfold_cv(train, v = 5)
```

```{r}
drug_recipe = recipe(Nicotine ~., train) %>%
  step_dummy(all_nominal(), -all_outcomes())

rf_model = rand_forest(mtry = tune(), min_n = tune(), trees = 100) %>% 
  set_engine("ranger", importance = "permutation") %>% 
  set_mode("classification")

drug_wflow = 
  workflow() %>% 
  add_model(rf_model) %>% 
  add_recipe(drug_recipe)


rf_grid = grid_regular(
  mtry(range = c(2, 8)), 
  min_n(range = c(5, 20)), 
  levels = 10
)

set.seed(123)
rf_res_tuned = tune_grid(
  drug_wflow,
  resamples = rf_folds,
  grid = rf_grid 
)
```


```{r 4v3}
rf_res_tuned %>%
  collect_metrics() %>%
  filter(.metric == "accuracy") %>%
  select(mean, min_n, mtry) %>%
  pivot_longer(min_n:mtry,
    values_to = "value",
    names_to = "parameter"
  ) %>%
  ggplot(aes(value, mean, color = parameter)) +
  geom_point(show.legend = FALSE) +
  facet_wrap(~parameter, scales = "free_x") +
  labs(x = NULL, y = "Accuracy")
```


```{r 4v4}

rf_res_tuned %>%
  collect_metrics() %>%
  filter(.metric == "accuracy") %>%
  mutate(min_n = factor(min_n)) %>%
  ggplot(aes(mtry, mean, color = min_n)) +
  geom_line(alpha = 0.5, size = 1.5) +
  geom_point() +
  labs(y = "Accuracy")
```

```{r Task 5v1}
best_rf = select_best(rf_res_tuned, "accuracy")

final_rf = finalize_workflow(
  drug_wflow,
  best_rf
)

final_rf
```

```{r Task 5v2}
final_rf_fit = fit(final_rf, train)
```

```{r Taskv3}
final_rf_fit %>% pull_workflow_fit() %>% vip(geom = "point")
```

The variables that are most important to the model are SS and Country, specifically UK. Oscore also appears to be of importance.

```{r Task 6v1}

trainpredrf = predict(final_rf_fit, train)
confusionMatrix(trainpredrf$.pred_class, train$Nicotine, 
                positive = "Yes")
```

```{r Task6v2}

testpredrf = predict(final_rf_fit, test)
confusionMatrix(testpredrf$.pred_class, test$Nicotine, 
                positive = "Yes")

```

On the training set, the model performs great with an accuracy of about 91%. Much better than the no information rate of only 67%. While the testing model only has an accuracy of about 74% and a no information rate of again 67%. However, it is not steady as there is quite a difference in accuracy between the two sets.

This model would be great when it comes to marketing nicotine products. Being able to see what variables are important can help dictate where marketing funds get spent. For example, in this case we see that the UK is less likely to consume nicotine products. So this can maybe help a company decide whether they should invest more money there, or if they are better off putting their focus elsewhere. I would hesitate recommending this model for real world use because it does not appear to be too steady. My concerns would be that you misinterpret who is using nicotine.
